Variational Inference for Inverse Reinforcement Learning with Gaussian Processes

### 2019-03-21 mpaper/paper.tex
Relevant work -- quite short, but I only kept the interesting bits

IRL is an important problem because adjusting the reward function by hand is
often unwieldy, since human behaviour often depends on many factors in
complicated ways
\cite{DBLP:conf/icml/PieterN04,DBLP:journals/corr/abs-1806-06877}. Moreover,
learning the reward function rather than the policy itself makes the model more
transferable to new environments---a minor change in the environment can
reorganise the whole policy but only have a local effect in the reward structure
\cite{DBLP:journals/corr/abs-1806-06877,DBLP:conf/uai/JinDAS17,DBLP:conf/nips/LevinePK11}.
IRL has been used to teach helicopters how to perform tricks
\cite{DBLP:conf/nips/AbbeelCQN06}, predict taxi destinations
\cite{DBLP:conf/huc/ZiebartMDB08}, and make driving safer and more efficient by
predicting pedestrian movement \cite{DBLP:conf/iros/ZiebartRGMPBHDS09} and the
driver's intentions \cite{DBLP:conf/aaai/VogelRGR12}.

% TODO: need to rewrite the first sentence
However, most IRL models in the literature make a convenient yet unjustified
assumption that the reward function can be expressed as a linear combination of
features
\cite{DBLP:conf/icml/PieterN04,DBLP:conf/uai/NeuS07,DBLP:conf/icml/NgR00,ziebart2008maximum}.
This assumption makes the models unable to represent many reward structures. Out
of the non-linear models proposed to date, none can answer the questions posed
in the first paragraph. Quite often, the models assume that rewards have no
variance \cite{DBLP:conf/nips/LevinePK11,DBLP:conf/uai/JinDAS17}. In this paper,
we show how that assumption can be lifted by switching from maximum likelihood
estimation to \emph{variational inference} (VI), i.e., we approximate the
posterior distribution of the model by optimising the parameters of a simpler
distribution to make it similar to the posterior. This approach can prove useful
in four major ways:
\begin{enumerate}
\item By working with full distributions instead of point estimates, we can
  expect more precise reward predictions.
\item Variance estimates can be used to guide what data should be collected
  next, i.e., if the rewards of some states have abnormally high variance, we
  might want to expose the model to more data visiting those and surrounding
  states.
\item Variances estimates can also be used to judge whether we can trust the
  predictions of the model or, perhaps, the model could benefit from some
  adjustments or more data.
\item By adopting a more Bayesian approach, we automatically incorporate Occam's
  razor into the model that guards against overfitting
  \cite{DBLP:conf/uai/JinDAS17}.
\end{enumerate}

@@

We keep the covariance function the same as in the work by Levine et al.
\cite{DBLP:conf/nips/LevinePK11}, which is a version of the automatic relevance
detection kernel \cite{DBLP:conf/nips/LevinePK11,neal2012bayesian}:
\begin{align*}
  k(\mathbf{x}_i, \mathbf{x}_j) = \lambda_0\exp\left( \vphantom{\frac{1}{2}} \right. &-\frac{1}{2}(\mathbf{x}_i - \mathbf{x}_j)^\intercal\bm\Lambda(\mathbf{x}_i - \mathbf{x}_j) \\
                                                                                     &- \mathbbm{1}[i \ne j]\sigma^2\tr(\bm\Lambda) \left. \vphantom{\frac{1}{2}} \right).
\end{align*}
Here, $\lambda_0$ is the overall `scale' factor for how similar or distant the
states are, $\bm\Lambda = \diag(\lambda_1, \dots, \lambda_d)$ is a diagonal
matrix that determines the relevance of each feature (where $d$ denotes the
number of features), $\mathbbm{1}$ is defined as
\[
  \mathbbm{1}[b] = \begin{cases}
    1 & \mbox{if $b$ is true} \\
    0 & \mbox{otherwise},
  \end{cases}
\]
and $\sigma^2$ is set to $10^{-2}/2$ (as the original paper noted that
the value makes little difference to the performance of the algorithm
\cite{DBLP:conf/nips/LevinePK11}). We will write $\bm\lambda = (\lambda_0,
\dots, \lambda_d)^\intercal$ to refer to both $\lambda_0$ and $\bm\Lambda$ at
the same time.

@@

It remains to decide on the model for $\mathbf{u}$ and $\mathbf{r}$. As is
commonly done when applying VI to GPs, we set
\begin{equation} \label{eq:approximation}
  \approximation = q(\mathbf{u}) q(\mathbf{r} \mid \mathbf{u}),
\end{equation}
where $q(\mathbf{r} \mid \mathbf{u}) = p(\mathbf{r} \mid \mathbf{u})$ and
$q(\mathbf{u}) = \mathcal{N}(\mathbf{u}; \bm\mu, \bm\Sigma)$
\cite{DBLP:conf/nips/ChengB17}.

@@

    \draw [->] (perturbation) edge (lemma3);
    \draw [->] (lebesgue) edge (theorem);
    \draw [->] (derivatives) edge (lemma1);
    \draw [->] (derivatives) edge (lemma2);
    \draw [->] (derivatives) edge (lemma3);
    \draw [->] (measurability) edge (theorem);
    \draw [->] (boundedness) edge (theorem);
    \draw [->] (lemma1) edge (theorem);
    \draw [->] (lemma2) edge (theorem);
    \draw [->] (lemma3) edge (theorem);
    \draw [->] (lemma4) edge (theorem);
  \end{tikzpicture}
  \caption{A graphical representation of dependencies between our theoretical
    results. An arrow from $A$ to $B$ means that $A$ was used to prove $B$.
    Results from the literature are in gray.}
  \label{fig:theorems}
\end{figure}

@@

Our main theorem is a specialised version of an integral differentiation result
by Chen \cite{lecture_notes}.
\begin{theorem} \label{thm:main}
  Whenever the derivative exists,
  \[
    \dt\iint
    \V(s)q(\mathbf{r} \mid \mathbf{u})q(\mathbf{u})\dx
    = \iint
    \dt[\V(s)q(\mathbf{r} \mid \mathbf{u})q(\mathbf{u})]\dx,
  \]
  where $t$ is any scalar part of $\bm\mu$, $\bm\Sigma$, or $\bm\lambda$.
\end{theorem}
\begin{proof}
  Let
  \begin{align*}
    \f &= \V(s)q(\mathbf{r} \mid \mathbf{u})q(\mathbf{u}), \\
    F(t) &= \iint \f\dx,
  \end{align*}
  and fix the value of $t$. Let $(t_n)_{n=1}^\infty$ be any sequence such that
  $\lim_{n \to \infty} t_n = t$, but $t_n \ne t$ for all $n$. We want to show
  that
  \begin{equation} \label{eq:to_prove}
    F'(t) = \lim_{n \to \infty} \frac{F(t_n) - F(t)}{t_n - t} = \iint \df\dx.
  \end{equation}
  We have
  \[
    \begin{split}
      \frac{F(t_n) - F(t)}{t_n - t} &= \iint \frac{\ftn - \f}{t_n - t}\dx \\
      &= \iint \fn\dx,
    \end{split}
  \]
  where
  \[
    \fn = \frac{\ftn - \f}{t_n - t}.
  \]
  Since
  \[
    \lim_{n \to \infty} \fn = \df,
  \]
  \eqref{eq:to_prove} follows from Theorem \ref{thm:lebesgue} as soon as we show
  that both $f$ and $f_n$ are measurable and find a non-negative integrable
  function $g$ such that for all $n$, $\mathbf{r}$, $\mathbf{u}$,
  \[
    |\fn| \le \g.
  \]
  The MDP value function is measurable by Proposition \ref{thm:measurability}.
  The result of multiplying or adding measurable functions (e.g., probability
  density functions) to a measurable function is still measurable. Thus,
  both $f$ and $f_n$ are measurable.

@@

\section{Related Work} % 0.5-1 page
% TODO: rewrite and make this section smaller

% apprenticeship learning, imitation learning
%a problem proposed by Russell in 1998 \cite{DBLP:conf/colt/Russell98}

As mentioned in the introduction, most IRL algorithms assume that the reward
function can be represented as a linear combination of features. This assumption
originated in one of the earliest papers on the topic by Ng and Russell
\cite{DBLP:conf/icml/NgR00}, which introduced several linear programming
approaches to the problem. The authors also noticed that often
multiple reward functions can explain the same behaviour, and suggested
heuristics for reward functions that are `far away' from reward functions that
do not fit the data.

A few years later, Abbeel and Ng \cite{DBLP:conf/icml/PieterN04} developed an
algorithm for the same formulation of the problem with a guarantee to converge
quickly. Neu and Szepesv\'ari \cite{DBLP:conf/uai/NeuS07} identified a weakness
in Abbeel and Ng's approach: the algorithm requires features to be
`appropriately' scaled, and optimal scaling may not be known. Instead, they
suggest a way to combine IRL with \emph{apprenticeship learning}, i.e., a
supervised learning task for optimal \emph{policy} recovery (whereas IRL focuses
on recovering the reward function).

Ramachandran and Amir \cite{DBLP:conf/ijcai/RamachandranA07} were the first to
formulate IRL in terms of Bayesian learning. While the model is easily
interpretable and able to handle experts that make mistakes, the algorithm can
only handle small state spaces and requires Monte Carlo Markov Chain (MCMC)
sampling for inference.

Ziebart et al. \cite{ziebart2008maximum} keep the linearity assumption, but
introduce an influential idea: resolving the ambiguity when multiple reward
functions explain the data by appealing to the maximum entropy principle.

Choi and Kim \cite{DBLP:conf/ijcai/ChoiK13} extend the Bayesian model to learn
good features as well as the reward function, trying to overcome the limitation
of linearity. However, the approach is quite limiting: all features are assumed
to have Boolean values, and the algorithm simply learns their conjunctions.

Levine et al. \cite{DBLP:conf/nips/LevinePK11} are the first to suggest a way to
learn nonlinear reward functions without harsh restrictions on the problem
domain by using GPs. We base our work primarily on their paper, and the
weaknesses we hope to address have already been covered in the previous section.
A recent extension to their work by Jin et al. \cite{DBLP:conf/uai/JinDAS17}
aims to harness the power of deep learning by using several layers of GPs,
making the model less dependent on being provided good features. They also use
VI, but with a few simplifying assumptions: deterministic training conditional
for the reward vector, and fully independent training conditional for the latent
state.

Finally, instead of using GPs to model nonlinear reward functions, one can use a
neural network (NN), as demonstrated by Wulfmeier et al.
\cite{wulfmeier2015maximum}. Their approach benefits from constant time
inference and the ability to learn complex features either from already-given
features or even from raw data. The only disadvantage (as demonstrated in the
paper) is that NNs converge slower than GPs (as measured by the number of
demonstrations).

\subsection{Variational Inference}

Variational inference has seen a recent increase in interest among academics,
with different approaches focusing on different goals: better time complexity,
handling a wider variety of models, making approximations more accurate, and
using more complex function approximation techniques (such as NNs)
to infer local latent variable values without having to calculate them
individually for each data point \cite{DBLP:journals/corr/abs-1711-05597}. As
our IRL model is based on a GP, we will begin by reviewing some of the VI
approaches applied specifically to GP regression. Based on a recent review of
scalable GPs \cite{DBLP:journals/corr/abs-1711-05597}, we will concentrate on
\emph{stochastic variational sparse approximations}, as they have achieved
modelling accuracy close to that of the full GP with no approximations, with
many methods providing a time complexity of $\mathcal{O}(m^3)$. Below we provide
a short overview of various assumptions that have been used in approximating
\emph{sparse} GPs (i.e., GPs that use inducing points), following on a paper by
Qui\~{n}onero-Candela and Rasmussen \cite{DBLP:journals/jmlr/CandelaR05}.

For many of the variables in our model (including the inducing points and the
hyperparameters of the covariance function), we have three possible ways of
handling them:
\begin{itemize}
\item Provide a full Bayesian treatment by defining a prior probability
  distribution. While this option can easily prevent overfitting, the choice of
  prior can be difficult to justify.
\item Fix the value of the variable. We can then optimise the value outside of
  the main algorithm, e.g., by running the algorithm with a set of possible
  values and keeping the value that produces the best performance. This option
  can be slow if we are interested in finding the optimal value, but could be
  appropriate if the variable has little impact on the algorithm's performance.
\item Treat the variable as a variational parameter. This method will
  efficiently optimise the value of the variable, but is vulnerable to
  overfitting. Furthermore, this requires us to find the derivative of the ELBO
  w.r.t. the variable, which could be difficult.
\end{itemize}

Titsias \cite{DBLP:journals/jmlr/Titsias09} is the first to suggest a
variational approximation where inducing points are treated as variational
parameters. The paper has influenced many of the later works covered in this
section, and has been reformulated by Gal et al. \cite{DBLP:conf/nips/GalWR14}
into a distributed algorithm. We will fix the inducing points for the baseline
version of our algorithm, but keep the idea in mind for possible future work.

Hensman et al. \cite{DBLP:conf/uai/HensmanFL13} reduce the complexity from
$\mathcal{O}(nm^2)$ to $\mathcal{O}(m^3)$ using a stochastic variational
inference (SVI) approach. While results such as efficiently computable natural
gradients and analytically tractable optimal solutions for variational
parameters are unlikely to transfer to a different problem domain, the overall
SVI framework and an approximating Gaussian distribution for $\mathbf{u}$ will
play an important role in our proposal.

Cheng and Boots \cite{DBLP:conf/nips/ChengB17} suggest using different bases in
the reproducing kernel Hilbert space for the mean and covariance functions.
The paper makes few assumptions and mostly relies on the work of
Titsias \cite{DBLP:journals/jmlr/Titsias09}, making it seem transferable to a
new domain. However, applying the idea to IRL is likely to be beyond the scope
of the project.

The variational Fourier features (VFF) algorithm by Hensman et al.
\cite{DBLP:journals/jmlr/HensmanDS17} is only defined for Mat\'ern kernels,
which is likely to be too restrictive for our situation (the original paper on
using GPs for IRL \cite{DBLP:conf/nips/LevinePK11} used the automatic relevance
detection kernel that has weights controlling how important each feature is).
While extending VFF to support a flexible class of kernels defined by Wilson and
Adams \cite{pmlr-v28-wilson13} is an interesting and promising avenue of work,
it is likely to be beyond the scope of this project as well.

While Peng et al. \cite{DBLP:conf/icml/PengZZQ17} provide a highly efficient
distributed implementation, the derivation of the ELBO relies primarily on the
fact that the evidence for a GP is a Gaussian, while in our case the evidence is
anything but. Hence, it is unlikely that the ideas from this paper could be
applicable to our IRL model.

Finally, since we expect $\posterior$ to be highly irregular, we would like our
approximation to be capable of representing a wide range of possible probability
distributions. The primary way of representing complex posteriors in VI is by
using \emph{normalising flows}, i.e., a collection of invertible
functions---parametrised by additional variational parameters---that are applied
to latent variables \cite{DBLP:conf/icml/RezendeM15}. Normalising flows, along
with some of the ideas mentioned previously, could provide great benefits to the
GP IRL VI model. However, we are forced to keep any non-essential features as
possible future work in order to make the project feasible in a given time
frame. Furthermore, note that due to various differences between regression and
IRL, we cannot simply apply a GP VI model as a whole. Instead, smaller tricks
and ideas from various papers can (and will) be used throughout the project.

@@

\subsection{Further Work}
% How much does a reward have to change to change the policy? Could be an
% interesting use case for variance predictions.

@@

>>>>

IRL is an important problem because adjusting the reward function by hand is
often unwieldy, since human behaviour often depends on many factors in
complicated ways
\cite{DBLP:conf/icml/PieterN04}. Moreover,
learning the reward function rather than the policy itself makes the model more
transferable to new environments---a minor change in the environment can
reorganise the whole policy but only have a local effect in the reward structure
\cite{DBLP:conf/uai/JinDAS17,DBLP:conf/nips/LevinePK11}.
IRL has been used to teach helicopters how to perform tricks
\cite{DBLP:conf/nips/AbbeelCQN06}, predict taxi destinations
\cite{DBLP:conf/huc/ZiebartMDB08}, and make driving safer and more efficient by
predicting pedestrian movement \cite{DBLP:conf/iros/ZiebartRGMPBHDS09} and the
driver's intentions \cite{DBLP:conf/aaai/VogelRGR12}.

% TODO: need to rewrite the first sentence
However, most IRL models in the literature make a convenient yet unjustified
assumption that the reward function can be expressed as a linear combination of
features
\cite{DBLP:conf/icml/PieterN04,DBLP:conf/icml/NgR00,ziebart2008maximum}.
This assumption makes the models unable to represent many reward structures. Out
of the non-linear models proposed to date, none can answer the questions posed
in the first paragraph. Quite often, the models assume that rewards have no
variance \cite{DBLP:conf/nips/LevinePK11,DBLP:conf/uai/JinDAS17}. In this paper,
we show how that assumption can be lifted by switching from maximum likelihood
estimation to \emph{variational inference} (VI), i.e., we approximate the
posterior distribution of the model by optimising the parameters of a simpler
distribution to make it similar to the posterior. This approach can prove useful
in four major ways:
\begin{enumerate}
\item By working with full distributions instead of point estimates, we can
  expect more precise reward predictions.
\item Variance estimates can be used to guide what data should be collected
  next, i.e., if the rewards of some states have abnormally high variance, we
  might want to expose the model to more data visiting those and surrounding
  states.
\item Variances estimates can also be used to judge whether we can trust the
  predictions of the model or, perhaps, the model could benefit from some
  adjustments or more data.
\item By adopting a more Bayesian approach, we automatically incorporate Occam's
  razor into the model that guards against overfitting
  \cite{DBLP:conf/uai/JinDAS17}.
\end{enumerate}

@@

We keep the covariance function the same as in the work by Levine et al.
\cite{DBLP:conf/nips/LevinePK11}, which is a version of the automatic relevance
detection kernel \cite{DBLP:conf/nips/LevinePK11}:
\begin{align*}
  k(\mathbf{x}_i, \mathbf{x}_j) = \lambda_0\exp\left( \vphantom{\frac{1}{2}} \right. &-\frac{1}{2}(\mathbf{x}_i - \mathbf{x}_j)^\intercal\bm\Lambda(\mathbf{x}_i - \mathbf{x}_j) \\
                                                                                     &- \mathbbm{1}[i \ne j]\sigma^2\tr(\bm\Lambda) \left. \vphantom{\frac{1}{2}} \right).
\end{align*}
Here, $\lambda_0$ is the overall `scale' factor for how similar or distant the
states are, $\bm\Lambda = \diag(\lambda_1, \dots, \lambda_d)$ is a diagonal
matrix that determines the relevance of each feature (where $d$ denotes the
number of features), $\mathbbm{1}$ is defined as
\[
  \mathbbm{1}[b] = \begin{cases}
    1 & \mbox{if $b$ is true} \\
    0 & \mbox{otherwise},
  \end{cases}
\]
and $\sigma^2$ is set to $10^{-2}/2$ (as the original paper noted that
the value makes little difference to the performance of the algorithm
\cite{DBLP:conf/nips/LevinePK11}). We will write $\bm\lambda = (\lambda_0,
\dots, \lambda_d)^\intercal$ to refer to both $\lambda_0$ and $\bm\Lambda$ at
the same time.

@@

It remains to decide on the model for $\mathbf{u}$ and $\mathbf{r}$. As is
commonly done when applying VI to GPs \cite{DBLP:conf/nips/ChengB17}, we set
\begin{equation} \label{eq:approximation}
  \approximation = q(\mathbf{u}) q(\mathbf{r} \mid \mathbf{u}),
\end{equation}
where $q(\mathbf{r} \mid \mathbf{u}) = p(\mathbf{r} \mid \mathbf{u})$ and
$q(\mathbf{u}) = \mathcal{N}(\mathbf{u}; \bm\mu, \bm\Sigma)$

@@

    \draw [->] (perturbation) edge (lemma3);
    \draw [->] (perturbation) edge (lemma1);
    \draw [->] (lebesgue) edge (theorem);
    \draw [->] (derivatives) edge (lemma1);
    \draw [->] (derivatives) edge (lemma2);
    \draw [->] (derivatives) edge (lemma3);
    \draw [->] (measurability) edge (theorem);
    \draw [->] (boundedness) edge (theorem);
    \draw [->] (lemma1) edge (theorem);
    \draw [->] (lemma2) edge (theorem);
    \draw [->] (lemma3) edge (theorem);
    \draw [->] (lemma4) edge (theorem);
  \end{tikzpicture}
  \caption{A graphical representation of dependencies between our theoretical
    results. An arrow from $A$ to $B$ means that $A$ was used to prove $B$.
    Results from the literature are in gray.}
  \label{fig:theorems}
\end{figure}

@@

Our main theorem is a specialised version of an integral differentiation result
by Timoney \cite{lecture_notes}.
\begin{theorem} \label{thm:main}
  Whenever the derivative exists,
  \[
    \dt\iint
    \V(s)q(\mathbf{r} \mid \mathbf{u})q(\mathbf{u})\dx
    = \iint
    \dt[\V(s)q(\mathbf{r} \mid \mathbf{u})q(\mathbf{u})]\dx,
  \]
  where $t$ is any scalar part of $\bm\mu$, $\bm\Sigma$, or $\bm\lambda$.
\end{theorem}
\begin{proof}
  Let
  \begin{align*}
    \f &= \V(s)q(\mathbf{r} \mid \mathbf{u})q(\mathbf{u}), \\
    F(t) &= \iint \f\dx,
  \end{align*}
  and fix the value of $t$. Let $(t_n)_{n=1}^\infty$ be any sequence such that
  $\lim_{n \to \infty} t_n = t$, but $t_n \ne t$ for all $n$. We want to show
  that
  \begin{equation} \label{eq:to_prove}
    F'(t) = \lim_{n \to \infty} \frac{F(t_n) - F(t)}{t_n - t} = \iint \df\dx.
  \end{equation}
  We have
  \[
    \begin{split}
      \frac{F(t_n) - F(t)}{t_n - t} &= \iint \frac{\ftn - \f}{t_n - t}\dx \\
      &= \iint \fn\dx,
    \end{split}
  \]
  where
  \[
    \fn = \frac{\ftn - \f}{t_n - t}.
  \]
  Since
  \[
    \lim_{n \to \infty} \fn = \df,
  \]
  \eqref{eq:to_prove} follows from Theorem \ref{thm:lebesgue} as soon as we show
  that both $f$ and $f_n$ are measurable and find a non-negative integrable
  function $g$ such that for all $n$, $\mathbf{r}$, $\mathbf{u}$,
  \[
    |\fn| \le \g.
  \]
  The MDP value function is measurable by Proposition \ref{thm:measurability}.
  The result of multiplying or adding measurable functions (e.g., probability
  density functions) to a measurable function is still measurable. Thus,
  both $f$ and $f_n$ are measurable.

@@

\section{Related Work} % 0.5-1 page

The IRL problem itself was originally proposed by Russell in 1998
\cite{DBLP:conf/colt/Russell98}. Most of the early approaches had the
aforementioned reward linearity assumption. One of the first papers on the
subject by Ng and Russell \cite{DBLP:conf/icml/NgR00} introduced several linear
programming algorithms and identified an important issue: there are typically
many reward functions that can explain the data equally well. This problem was
solved by Ziebart et al. \cite{ziebart2008maximum} with the introduction of IRL
based on the principles of maximum causal entropy in a linearly-solvable MDP.

Levine et al. \cite{DBLP:conf/nips/LevinePK11} were the first to lift the
linearity assumption without imposing additional restrictions on the problem.
They do, however, model rewards as having no variance---our work removes this
restriction without any compromises.

Recently, Jin et al. \cite{DBLP:conf/uai/JinDAS17} have adapted the model
proposed by Levine et al. \cite{DBLP:conf/nips/LevinePK11} to use deep GPs,
harnessing the power of deep learning to make the model less dependent on what
features are provided. Although they use VI, their approximating distribution
for rewards at inducing points is simply the Dirac $\delta$ function, which is
essentially equivalent to the assumption of no variance.

An alternative to GPs for modelling nonlinear functions is, of course, neural
networks. Wulfmeier et al. \cite{wulfmeier2015maximum} have shown how they can
be used in the IRL setting. While this approach benefits from constant-time
inference and the ability to learn complex features from data, neural
networks often need significantly more data for the weights across all layers to
stabilise.

\subsection{Variational Inference}
% none of these approaches really work in our situation because they tend to
% depend on properties of how GPs are used in regression that are no longer true
% in IRL

Since the focus of our work was on proving feasibility rather than ensuring
performance, we simply used a combination of Gaussians for our variational
approximation. However, while VI was initially focused on approximating
distributions using simplistic models where all variables are independent
\cite{blei2017variational}, the last few years have brought many advances in
approximating more complex distributions and greatly reducing the computational
complexity of the task. Adapting some of them to IRL is a nontrivial but highly
valuable undertaking.

For approximating complex distributions, Rezende and Mohamed
\cite{DBLP:conf/icml/RezendeM15} suggest using \emph{normalising flows}, i.e., a
collection of invertible functions---parametrised by additional variational
parameters---that are applied to latent variables. A major challenge in applying
their work to IRL is related to variational parameters being used to compute the
MDP value function, i.e., how can we take the derivative of the value function
with respect to such a variational parameter? Alternatively, perhaps one can
construct a different model that would make this question moot.

Another approach to flexibility in modelling could come from considering
different GP kernels. For instance, Wilson and Adams \cite{pmlr-v28-wilson13}
show how all \emph{stationary} (i.e., invariant to translations) kernels can be
generated (or at least approximated) from a mixture of Gaussians in their
spectral representation using Bochner's theorem
\cite{bochner1959lectures,DBLP:journals/technometrics/Woodard00}. It looks
promising to combine these kernels with the variational Fourier features
approach by Hensman et al. \cite{DBLP:journals/jmlr/HensmanDS17} that leverages
the same spectral representations for efficient VI.

@@

\subsection{Further Work}

@@

Finally, building on the idea that variance estimates can be used to judge
whether the model has learned optimal policy, an interesting question for
MDP (or, perhaps, dynamical systems) research would be: how much does a reward
have to change in order to affect the deterministic policy? A simple answer to
this question would allow us to use variance estimates in order to quantify the
model's confidence regarding optimal behaviour.
